---
title: "Deep Learning"
author: "João Victor Barroso Mafra"
date: "14 de março de 2018"
output: html_document
---

```{r setup, include=FALSE}
library(tensorflow)
library(keras)
library(corrplot)

```


 
```{r}
# Read in `iris` data
iris <- read.csv(url("http://archive.ics.uci.edu/ml/machine-learning-databases/iris/iris.data"), header = FALSE) 
```

Nomeando colunas...

The graph indicates a positive correlation between the Petal.Length and the Petal.Width for the different species of the iris flowers. However, this is something that you probably want to test with the cor() function, which will give you the overall correlation between all attributes that are included in the data set

```{r}
names(iris) <- c("Sepal.Length", "Sepal.Width", "Petal.Length", "Petal.Width", "Species")

plot(iris$Petal.Length, 
     iris$Petal.Width, 
     pch=21, bg=c("red","green3","blue")[unclass(iris$Species)], 
     xlab="Petal Length", 
     ylab="Petal Width")

cor(iris$Petal.Length, iris$Petal.Width)

```

Correlações entre todos os atributos

```{r}
# Store the overall correlation in `M`
M <- cor(iris[,1:4])

# Plot the correlation plot with `M`
corrplot(M, method="circle")
```

Pré-processamento:

Não necessita normalização.

All values of all the attributes of the Iris data set are contained within the range of 0.1 and 7.9, which you can consider acceptable.



```{r}

summary(iris)

```

Normalizando para avaliar efeitos:

```{r}

iris.norm <- iris
iris.norm[,5] <- as.numeric(iris.norm[,5]) -1

# Turn `iris` into a matrix
iris.norm <- as.matrix(iris.norm)

# Set iris `dimnames` to `NULL`
dimnames(iris.norm) <- NULL

iris.norm[,1:4] <- normalize(iris.norm[,1:4])

# Return the summary of `iris`
summary(iris.norm)
```


Divisão treino e teste.

```{r}

set.seed(500)

# Determine sample size
ind <- sample(2, nrow(iris), replace=TRUE, prob=c(0.67, 0.33))

# Split the `iris` data
iris.training <- iris[ind==1, 1:4]
iris.test <- iris[ind==2, 1:4]

# Split the class attribute
iris.trainingtarget <- iris[ind==1, 5]
iris.testtarget <- iris[ind==2, 5]

```

When you want to model multi-class classification problems with neural networks, it is generally a good practice to make sure that you transform your target attribute from a vector that contains values for each class value to a matrix with a boolean for each class value and whether or not a given instance has that class value or not.

```{r}
# One hot encode training target values
iris.trainLabels <- to_categorical(iris.trainingtarget)

# One hot encode test target values
iris.testLabels <- to_categorical(iris.testtarget)

```

Construindo o modelo, que tem como objetivo prever a especie de uma certa flor.

How the output layer creates 3 output values, one for each Iris class (versicolor, virginica or setosa). The first layer, which contains 8 hidden notes, on the other hand, has an input_shape of 4. This is because your training data iris.training has 4 columns.

```{r}
# Initialize a sequential model
model <- keras_model_sequential() 

# Add layers to the model
model %>% 
    layer_dense(units = 8, activation = 'relu', input_shape = c(4)) %>% 
    layer_dense(units = 4, activation = 'softmax')
```

Inspecionando o modelo:

```{r}
# Print a summary of a model
summary(model)

# Get model configuration
get_config(model)

# Get layer configuration
get_layer(model, index = 1)

# List the model's layers
model$layers

# List the input tensors
model$inputs

# List the output tensors
model$outputs
```

Compilando o modelo

```{r}
# Compile the model
model %>% compile(
     loss = 'categorical_crossentropy',
     optimizer = 'adam',
     metrics = 'accuracy'
 )

# Print a summary of a model
summary(model)

# Get model configuration
get_config(model)

# Get layer configuration
get_layer(model, index = 1)

# List the model's layers
model$layers

# List the input tensors
model$inputs

# List the output tensors
model$outputs
```


Ajustando o modelo para os dados.

```{r}
# Fit the model 
model %>% fit(
     as.matrix(iris.training), 
     iris.trainLabels, 
     epochs = 200, 
     batch_size = 5, 
     validation_split = 0.2
 )
```



















